---
title: "GLM NNL Database"
author: "Nicole Shumway"
date: "19 August 2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

#Install packages
```{r}
install.packages("Hmisc")
install.packages("MASS")
install.packages("AER")
install.packages("ggplot2")
install.packages("tidyverse")
install.packages("RColorBrewer")
install.packages("effects")
install.packages("ggrepel")
install.packages("extrafont")
install.packages("lsr")
install.packages("gridExtra")
install.packages("ggpubr")
install.packages("ggsignif")
```



#Load packages----
```{r setup}


library(Hmisc)
library(MASS)
library(AER)
library(ggplot2)
library(tidyverse)
library(RColorBrewer)
library(effects)
library(ggrepel)
library(extrafont)
library(lsr)
library(gridExtra)
library(ggpubr)
library(ggsignif)

```


##Load Data ---- work computer
```{r }


Policy_Analysis <- read.csv("C:/Users/uqnshumw/OneDrive - The University of Queensland/Documents/Git/Marine-NNL-database/Policy_Analysis.csv")


```

#Load data ---- laptop
```{r }

Policy_Analysis <- read.csv("~/Desktop/OneDrive - The University of Queensland/Documents/Git/Marine-NNL-database/Policy_Analysis.csv")
```

#Summary Information----

```{r}

summary(offsets_db$Scale)

scale <- offsets_db %>% 
  filter(Implicit_Explicit == "Explicit")
summary(scale$Scale)

regions <- offsets_db %>% 
  filter(Implicit_Explicit == "Explicit")

summary(regions$Region)

focus <- offsets_db %>% 
  filter(Implicit_Explicit == "Explicit")

summary(focus$Focus)

```

#Correlation Matrix----  ALL DATA
```{r}
head(Policy_Analysis)
Policy_data <- Policy_Analysis[,11:length(Policy_Analysis)] ## makes a new dataframe from policy analysis, subsets everything to the right of presence/absence
View(Policy_data)


round(cor(Policy_data, use = "na.or.complete"),2) ##rounds the date two decimal places for clarity
cor_matrix <- cor(Policy_data, use="pairwise.complete.obs", method = c("spearman"))   
View(cor_matrix)

```

#Ordinal Logistic Regression---- for Stage vs. ALL Policies
```{r}

#To describe or predict variables. OLR can id which variables predict the level of involvement in offsets policy

#Dividing data into training and test set
#Random sampling
#samplesize = .60*nrow(Policy_data)
#index = sample(seq_len(nrow(Policy_data)), size = samplesize)
#Creating training and test set 
#datatrain <- Policy_Analysis[index,]
#datatest <- Policy_Analysis[-index,]

#for complete separation problem:https://stats.stackexchange.com/questions/11109/how-to-deal-with-perfect-separation-in-logistic-regression

## Build ordinal logistic regression model

### Stage of Policy vs. ALL values ###


Policy_Analysis$STAGE2 = factor(Policy_Analysis$STAGE2, levels = c("0", "1", "2", "3", "4") )

All_Stage <- polr(Policy_Analysis$STAGE2 ~  Policy_Analysis$mam_bird  + Policy_Analysis$OHI  + log(Policy_Analysis$GDP) + Policy_Analysis$EEZ_Protected +
                      Policy_Analysis$Polity2, data = Policy_Analysis, Hess = TRUE) ##DRopped Richness and NRR not significant, EEZ dropped as causing glm.fit error: fitter prob 0 or 1 occured and increased AIC
summary(All_Stage) 
coeftest(All_Stage)

#confidence intervals
ci_All <- confint(All_Stage)


#After building the model and interpreting the model, the next step is to evaluate it. 
  #The evaluation of the model is conducted on the test dataset. A basic evaluation approach is to compute the confusion matrix and the misclassification error. 

#Compute confusion table and misclassification error - model predicts 0,1 bette
predictstage = predict(All_Stage,Policy_Analysis)
table(Policy_Analysis$STAGE2, predictstage)
mean(as.character(Policy_Analysis$STAGE2) != 
       as.character(predictstage))

#results - 42x 0 is identified correctly, 1 & 2 are never id'd correctly, 3 id'd 17x, 4 id'd correctly 6x - so good at predicting 0, 3 and 4, but not 1 and 2

```


#Stage vs all variables ---- Indiv variables
```{r}

stage_risk <- polr(Policy_Analysis$STAGE2 ~  Policy_Analysis$mam_bird, data = Policy_Analysis, Hess = TRUE)
summary(stage_risk) 
coeftest(stage_risk)
ci_stage_risk <-confint(stage_risk)
ci_stage_risk


EEZ_stage <- polr(Policy_Analysis$STAGE2 ~  Policy_Analysis$EEZ_Protected, data = Policy_Analysis, Hess = TRUE)
summary(EEZ_stage) 
coeftest(EEZ_stage)
ci_EEZ_stage <-confint(EEZ_stage)
ci_EEZ_stage



OHI_stage <- polr(Policy_Analysis$STAGE2 ~  Policy_Analysis$OHI, data = Policy_Analysis, Hess = TRUE)
summary(OHI_stage) 
coeftest(OHI_stage)
ci_OHI_stage <-confint(OHI_stage)
ci_OHI_stage


GDP_stage <- polr(Policy_Analysis$STAGE2 ~  log(Policy_Analysis$GDP), data = Policy_Analysis, Hess = TRUE)
summary(GDP_stage) 
coeftest(GDP_stage)
ci_GDP_stage <-confint(GDP_stage)
ci_GDP_stage



Polity_stage <- polr(Policy_Analysis$STAGE2 ~  log(Policy_Analysis$Polity2), data = Policy_Analysis, Hess = TRUE)
summary(Polity_stage) 
coeftest(Polity_stage)
Polity_stage <-confint(Polity_stage)
Polity_stage


```


# convert the coefficients---- into odds ratios
```{r} 

exp(coef(All_Stage))

#To get the Odds ratio (OR) and confidence intervals, we just exponentiate the estimates and confidence intervals

exp(cbind(OR = coef(All_Stage), ci_All))

```


#Testing for multicollinearity ----- Stage  
```{r} 

#https://cran.r-project.org/web/packages/olsrr/vignettes/regression_diagnostics.html

library(olsrr)

Policy_Analysis <- read.csv("C:/Users/uqnshumw/OneDrive - The University of Queensland/Documents/Git/Marine-NNL-database/Policy_Analysis.csv")

multico_model <- lm(Policy_Analysis$STAGE2 ~  Policy_Analysis$mam_bird +Policy_Analysis$EEZ_Protected +
                      Policy_Analysis$OHI + log(Policy_Analysis$GDP) + 
                      Policy_Analysis$Polity2 + Policy_Analysis$Richness, data = Policy_Analysis)

ols_vif_tol(multico_model)
multico_model

```



#Plotting the effects ---- All_Stage
```{r}
ar <- profile(All_Stage)
plot(ar)
pairs(ar)

```


#Ordinal Logistic Regression---- for Policy inclusion vs predictors
```{r}

#To describe or predict variables. OLR can id which variables predict the level of involvement in offsets policy

#https://stats.idre.ucla.edu/r/dae/ordinal-logistic-regression/

#Dividing data into training and test set
#Random sampling
#samplesize = .60*nrow(Policy_data)
#index = sample(seq_len(nrow(Policy_data)), size = samplesize)
#Creating training and test set 
#datatrain <- Policy_Analysis[index,]
#datatest <- Policy_Analysis[-index,]



## Build ordinal logistic regression model

### Stage of Implementation vs. ALL values ###


Policy_Analysis$marine_mech = factor(Policy_Analysis$marine_mech, levels = c("0", "1", "2", "3"))

Inclusion_mech <- polr(Policy_Analysis$marine_mech ~  Policy_Analysis$mam_bird+ Policy_Analysis$OHI + log(Policy_Analysis$GDP) + Policy_Analysis$Polity2, data = Policy_Analysis, Hess = TRUE) ##DRopped Richness, EEZ and NRR not significant within the model

summary(Inclusion_mech) 
coeftest(Inclusion_mech)

#confidence intervals
ci_imp <-confint(Inclusion_mech)
ci_imp

#After building the model and interpreting the model, the next step is to evaluate it. 
  #The evaluation of the model is conducted on the test dataset. A basic evaluation approach is to compute the confusion matrix and the misclassification error. 

#Compute confusion table and misclassification error - model predicts 0,1 bette
predictstage = predict(Implementation_Stage,Policy_Analysis)
table(Policy_Analysis$marine_mech, predictstage)
mean(as.character(Policy_Analysis$marine_mech) != 
       as.character(predictstage))

```


# convert the coefficients into odds ratios -
```{r} 

exp(coef(Implementation_Stage))

#To get the Odds ratio (OR) and confidence intervals, we just exponentiate the estimates and confidence intervals

exp(cbind(OR = coef(Implementation_Stage), ci_imp))

```



#Testing for multicollinearity - Inclusion mechanism
```{r} 

#https://cran.r-project.org/web/packages/olsrr/vignettes/regression_diagnostics.html

library(olsrr)

multico_imp <- lm(Policy_Analysis$marine_mech ~  Policy_Analysis$mam_bird +Policy_Analysis$EEZ_Protected +
                      Policy_Analysis$OHI + log(Policy_Analysis$GDP) + 
                      Policy_Analysis$Polity2 + Policy_Analysis$Richness, data = Policy_Analysis)

ols_vif_tol(multico_imp)
View(multico_imp)

```



#Ordinal regression by factor ---- mech~Rents
```{r}
rent <- polr(Policy_Analysis$marine_mech ~  Policy_Analysis$Rents, data = Policy_Analysis, Hess = TRUE)
summary(rent) 
coeftest(rent)

ci_rent <-confint(rent)
ci_rent
```

#Ordinal regression by factor - EEZ
```{r}

EEZ_ord <- polr(Policy_Analysis$marine_mech ~  Policy_Analysis$EEZ_Protected, data = Policy_Analysis, Hess = TRUE)
summary(EEZ_ord) 
coeftest(EEZ_ord)

ci_EEZ_ord <-confint(EEZ_ord)
ci_EEZ_ord
```


#Ordinal regression by factor - richness
```{r}
rich <- polr(Policy_Analysis$marine_mech ~  Policy_Analysis$Richness, data = Policy_Analysis, Hess = TRUE)
summary(rich) 
coeftest(rich)

ci_rich <-confint(rich)
ci_rich

exp(coef(rich))

#To get the Odds ratio (OR) and confidence intervals, we just exponentiate the estimates and confidence intervals

exp(cbind(OR = coef(rich), ci_rich))
```


#Ordinal regression by factor - Redlist birds/mammals
```{r}
risk <- polr(Policy_Analysis$marine_mech ~  Policy_Analysis$mam_bird, data = Policy_Analysis, Hess = TRUE)
summary(risk) 
coeftest(risk)

ci_risk <-confint(risk)
ci_risk
```


#Ordinal regression by factor - Ocean Health Index
```{r}
health <- polr(Policy_Analysis$marine_mech ~  Policy_Analysis$OHI, data = Policy_Analysis, Hess = TRUE)
summary(health) 
coeftest(health)

ci_risk <-confint(health)
ci_risk
```

#Ordinal regression by factor - GDP
```{r}
wealth <- polr(Policy_Analysis$marine_mech ~  log(Policy_Analysis$GDP), data = Policy_Analysis, Hess = TRUE)
summary(wealth) 
coeftest(wealth)

ci_risk <-confint(wealth)
ci_risk
```

#Ordinal regression by factor - Polity2
```{r}
polity <- polr(Policy_Analysis$marine_mech ~  Policy_Analysis$Polity2, data = Policy_Analysis, Hess = TRUE)
summary(polity) 
coeftest(polity)

ci_risk <-confint(polity)
ci_risk
```

#Plotting the effects
```{r}

install.packages("effects")
library(effects)

Effect(focal.predictors = c("marine_mech","mam_bird"), Implementation_Stage)

```


#Plotting marine mech vs variables ---- Figure 1
```{r}

specific <- Policy_Analysis %>% 
  filter (marine_mech == 3)

explicit <- Policy_Analysis %>% 
  filter (marine_mech == 2)

implicit <- Policy_Analysis %>% 
  filter (marine_mech == 1)

none <- Policy_Analysis %>% 
  filter (marine_mech == 0)

group_names <- c('0' = "none",
                 '1' = "implicit",
                 '2' = "explicit",
                 '3' = "specific")

color_palette=c("grey30","#33FF99", "#00CC66", "#009933")

risk2 <- Policy_Analysis %>% 
  ggplot(aes(x = marine_mech, y = log(mam_bird))) +
  geom_boxplot(aes(fill = marine_mech), size = .75, outlier.shape = NA)+ 
  geom_point(position = "jitter", size =.5) +
  scale_fill_manual(values=color_palette) + # Boxplot fill color
  xlab("") +
  ylab("log(Threatened birds & mammals)")+
  scale_x_discrete(labels = group_names)+ 
  #ggtitle("Odds") +
  theme_classic()  

risk1 <- risk2 + theme(legend.position = "none",
                       axis.text.x = element_text(size=16), 
                       axis.text.y = element_text(size=16),
                       axis.title.y = element_text(size=16))
#risk <- risk1 + annotate("text", x= .9, y= -1, label = "p = 0.0002e-12")
risk1

health2 <- Policy_Analysis %>% 
  ggplot(aes(x = marine_mech, y = OHI)) +
  geom_boxplot(aes(fill = marine_mech), size = .75, outlier.shape = NA)+ 
  geom_point(position = "jitter", size =.5) +
  scale_fill_manual(values=color_palette) + # Boxplot fill color
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))+
  xlab("") +
  ylab("Ocean health index")+
  scale_x_discrete(labels = group_names)+ 
  #ggtitle("Odds") +
  theme_classic() 

health1 <- health2 + theme(legend.position = "none",
                           axis.text.x = element_text(size=16),
                           axis.text.y = element_text(size=16),
                           axis.title.y = element_text(size=16))
#health <- health1 + annotate("text", x= .75, y= 99, label = "p = 0.047")
health1

wealth2 <- Policy_Analysis %>% 
  ggplot(aes(x = marine_mech, y = log(GDP))) +
  geom_boxplot(aes(fill = marine_mech), size = .75, outlier.shape = NA)+ 
  geom_point(position = "jitter", size =.5) +
  scale_fill_manual(values=color_palette) + # Boxplot fill color
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))+
  xlab("") +
  ylab("log(GDP)")+
  scale_x_discrete(labels = group_names)+ 
  #ggtitle("Odds") +
  theme_classic()
wealth1 <- wealth2 + theme(legend.position = "none",
                           axis.text.x = element_text(size=16), 
                       axis.text.y = element_text(size=16),
                       axis.title.y = element_text(size=16))
#wealth <-wealth1 + annotate("text", x= .75, y= 30, label = "p = 0.0004")
wealth1

polity3 <- Policy_Analysis %>% 
  ggplot(aes(x = marine_mech, y = Polity2)) +
  geom_boxplot(aes(fill = marine_mech), size = .75, outlier.shape = NA)+ 
  geom_point(position = "jitter", size =.5) +
  scale_fill_manual(values=color_palette) + # Boxplot fill color
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))+
  xlab("") +
  ylab("Polity2")+
  scale_x_discrete(labels = group_names)+ 
  #ggtitle("Odds") +
  theme_classic()
polity1 <- polity3 + theme(legend.position = "none",
                           axis.text.x = element_text(size=16), 
                       axis.text.y = element_text(size=16),
                       axis.title.y = element_text(size=16))
#polity <- polity1 + annotate("text", x= .75, y= 12, label = "p = 0.49")
polity1
 
mech_plot <- ggarrange(risk1, wealth1, health1, polity1,
          labels = c("A", "B", "C", "D"),
          ncol = 2, nrow = 2,
          hjust = -5.5)
  


Figure1 <- annotate_figure(mech_plot,
                           bottom = text_grob("Inclusion mechanism",     
                                              color= "black", face = "bold", 
                                              size = 14))

Figure1
```

# Stage of Implementation vs variables - Figure 2
```{r}

stage_names <- c('0' = "none",
                 '1' = "potential",
                 '2' = "preliminary",
                 '3' = "in progress",
                 '4' = "established")

stage_risk2 <- ggplot(Policy_Analysis, aes(x = STAGE2, y = log(mam_bird))) +
  geom_boxplot(aes(fill = STAGE2), size = .75, outlier.shape = NA)+ 
  geom_point(position = "jitter", size =.5)  +
  #scale_fill_manual(values=color_palette) + # Boxplot fill color
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))+
  xlab("") +
  ylab("Threatened species")+
  scale_x_discrete(labels = stage_names)+ 
  theme_classic()

stage_risk <- stage_risk2 + theme(legend.position = "none",
                                   axis.text.x = element_text(size=15), 
                       axis.text.y = element_text(size=15),
                       axis.title.y = element_text(size=15))
#stage_risk <- stage_risk1 + 
  #annotate("text", x= .95, y= 0, label = "p = 2.2e-16")
stage_risk

stage_EEZ2 <-ggplot(Policy_Analysis, aes(x = STAGE2, y = log(EEZ_Protected))) +
  geom_boxplot(aes(fill = STAGE2), size = .75, outlier.shape = NA)+ 
  geom_point(position = "jitter", size = .5) +
  #scale_fill_manual(values=color_palette) + # Boxplot fill color
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))+
  xlab("") +
  ylab("log(EEZ Protected)")+
  scale_x_discrete(labels = stage_names)+ 
  theme_classic() 
stage_EEZ <- stage_EEZ2 + theme(legend.position = "none",
                                 axis.text.x = element_text(size=15), 
                       axis.text.y = element_text(size=15),
                       axis.title.y = element_text(size=15))
#stage_EEZ <- stage_EEZ1 + annotate("text", x= .9, y= 2, label = "p = 0.045")
stage_EEZ

stage_health2 <-ggplot(Policy_Analysis, aes(x = STAGE2, y = OHI)) +
  geom_boxplot(aes(fill = STAGE2), size = .75, outlier.shape = NA)+ 
  geom_point(position = "jitter", size =.5) +
  #scale_fill_manual(values=color_palette) + # Boxplot fill color
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))+
  xlab("") +
  ylab("Ocean Health Index")+
  scale_x_discrete(labels = stage_names)+ 
  #ggtitle("Odds") +
  theme_classic()
stage_health <- stage_health2+ 
                  theme(legend.position = "none",
                       axis.text.x = element_text(size=15), 
                       axis.text.y = element_text(size=15),
                       axis.title.y = element_text(size=15))
#stage_health <- stage_health1 + 
  #annotate("text", x= .85, y= 100, label = "p = 0.014")
stage_health 

stage_gdp2 <- ggplot(Policy_Analysis, aes(x = STAGE2, y = log(GDP))) +
  geom_boxplot(aes(fill = STAGE2), size = .75, outlier.shape = NA)+ 
  geom_point(position = "jitter", size =.5) +
  #scale_fill_manual(values=color_palette) + # Boxplot fill color
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))+
  xlab("") +
  ylab("log(GDP)")+
  scale_x_discrete(labels = stage_names)+ 
  #ggtitle("Odds") +
  theme_classic()
stage_gdp <-stage_gdp2 + 
            theme(legend.position = "none",
                      axis.text.x = element_text(size=15), 
                       axis.text.y = element_text(size=15),
                       axis.title.y = element_text(size=15))
#stage_gdp <- stage_gdp1 + annotate("text", x= .85, y= 30, label = "p = 0.045")
stage_gdp

stage_polity2 <- ggplot(Policy_Analysis, aes(x = STAGE2, y = Polity2)) +
  geom_boxplot(aes(fill = STAGE2), size = .75, outlier.shape = NA)+ 
  geom_point(position = "jitter", size =.5) +
  #scale_fill_manual(values=color_palette) + # Boxplot fill color
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))+
  xlab("") +
  ylab("Polity2")+
  scale_x_discrete(labels = stage_names)+ 
  #ggtitle("Odds") +
  theme_classic()
stage_polity <-stage_polity2+
            theme(legend.position = "none",
                  axis.text.x = element_text(size=15), 
                       axis.text.y = element_text(size=15),
                       axis.title.y = element_text(size=15))
#stage_polity <- stage_polity1 + annotate("text", x= .9, y= 12, label = "p = 0.0002")
stage_polity

stage_plot <- ggarrange(stage_risk, stage_EEZ, stage_health, stage_gdp, stage_polity,
          labels = c("A", "B", "C", "D", "E"),
          ncol = 2, nrow = 3, hjust = -5.5)

Figure2 <- annotate_figure(stage_plot, bottom = text_grob("Stage of Implementation", color= "black", face = "bold", size = 14, vjust = -1))

Figure2
```




```{r}
#Plotting the effects 
library("effects")
Effect(focal.predictors = "mam_bird",Implementation_Stage)
plot(Effect(focal.predictors = "OHI",Implementation_Stage))
plot(Effect(focal.predictors = c("mam_bird", "OHI"),Implementation_Stage))
```




#Marine specific variables
```{r}

## Marine Specific Policies ####
SubN_Pol <- Policy_Analysis %>%   ## Subsets marine specific subnational policies
  filter(Mar_subN == 3)
Nat_Pol <- Policy_Analysis %>%   ##subsets marine specific national policies
  filter(Mar_Nat ==3)
Org_Pol <- Policy_Analysis %>% 
  filter(Mar_org ==3)

marine_nat <- full_join(Nat_Pol, SubN_Pol)  #### joins the two together, all marine specific policies
marine_specific <- full_join(marine_nat, Org_Pol)

### Policies that are not marine specific, but include marine explicitly ####
Sub_exp <-Policy_Analysis %>%   ## Subsets marine explicit subnational policies
  filter(Mar_subN == 2)
Nat_exp <-Policy_Analysis %>%   ## Subsets marine explicit subnational policies
  filter(Mar_Nat == 2)
Org_exp <- Policy_Analysis %>% 
  filter(Mar_org == 2)

marine_nat2 <- full_join(Sub_exp, Nat_exp)
marine_explicit <- full_join(marine_nat2, Org_exp)


## Policies that include marine implicitly ###

marine_implicit <- Policy_Analysis %>% 
  filter(Mar_subN == 1 | Mar_Nat == 1 |Mar_supraN == 1 | Mar_org == 1)

Sub_imp <-Policy_Analysis %>%   ## Subsets marine implicit subnational policies
  filter(Mar_subN == 1 )
Nat_imp <-Policy_Analysis %>%   ## Subsets marine implicit national policies
  filter(Mar_Nat == 1)
Supr_imp <- Policy_Analysis %>%   ## Subsets marine implicit supra-national policies
 filter(Mar_supraN == 1)
Mar_Imp <- full_join (Sub_imp, Nat_imp)
marine_implicit2 <- full_join (Mar_Imp, Supr_imp)  ##all marine implicit policies


#as.factor(MarinePol$STAGE2)

#marine_inclusive <- full_join(marine_specific, marine_explicit)  ### Includes marine considered explicitly and implicitly

#All_marine <- full_join(marine_inclusive, marine_specific) ## Include all marine policies, no matter how included

## Policies that don't include marine at all
No_mar <- Policy_Analysis %>%   #Subsets no policies
  filter(Presence_Absence == 0)


```

#Marine Policies from offsets database
```{r}
#load data
offsets_db <- read.csv("C:/Users/uqnshumw/OneDrive - The University of Queensland/Documents/Git/Marine-NNL-database/Offsets by country.csv", comment.char="#")

sp_policy <- offsets_db %>% 
  filter(Marine.Specific == "Yes")


#Filter db by marine specific policies

#filters by country
specific <- Policy_Analysis %>% 
  filter(marine_mech == "3")


#filters by country (n=36)

specific_explicit <- Policy_Analysis %>% 
  filter(marine_mech == "2" | marine_mech == "3")

explicit <- Policy_Analysis %>% 
  filter(marine_mech == "2")

##Implicit policies
implicit <- Policy_Analysis %>% 
  filter(marine_mech == "1")

none <- Policy_Analysis %>% 
  filter(marine_mech == "0")


##group implicit to all explicit policies - this gives you 90 policies, how many countries though?
#ALL <- offsets_db %>% 
  #filter(Implicit_Explicit == "Explicit"| Implicit_Explicit == "Implicit")

# this subsets by the number of disctinct countries n=71 (added one)
by_country2 <- ALL %>% 
  distinct(Country, .keep_all = FALSE) 

```


#By type of policy
```{r}

#marine specific policies focus on Biodiversity (n=4), Mangrove or Seagrass (n=3), marine ecosystems (n=2), Fish (n=1)
summary(specific$Focus)

#marine explicit policies
policy_type_exp <-offsets_db %>% 
  filter(Marine.Specific == "No") %>% 
  filter(marine.included == "Yes") %>% 
  filter(Implicit_Explicit == "Explicit")

##marine explicit policies focus on Biodiversity (n=23), Wetlands or Mangroves (n=11), Coastal or marine environments (n=8), Fish
sum_exp <-summary(policy_type_exp$Focus)

View(sum_exp)
```

#Summary stats for marine policies as tables----
```{r}

ggplot(Policy_Analysis, aes(x = marine_mech)) +
  geom_bar(stat = 'count') +
  theme(axis.text.x = element_text(angle = 45, size = 7.5, hjust = 1)) +
  xlab("Policy Type") +
  ylab("Number of countries") +
  labs(fill = "Mine Type")+
  facet_wrap(~, labeller = as_labeller(marine_names))
  

#Makes a vector with mine type names
marine_names <- c('0' = "No policy",
                 '1' = "Marine implicit",
                 '2' = "Marine explicit",
                 '3' = "Marine specific") 

grid.table(for_table)

```

##Subset variables for analysis----
```{r}

Var_subset <- Policy_Analysis %>% 
  select(marine_mech, Richness, GDP, EEZ_Protected, OHI, mam_bird, Rents, Polity2)


Offset_subset <- offsets_db %>% 
  select(Country, Region, Marine.Specific, Implicit_Explicit, Focus, Year, Stage)
  

```



## Marine Specific vs OHI ----
```{r}

########Plot marine specific policies vs OHI #################

install.packages("reshape2")
library(reshape2)



Policy_Analysis$marine_mech = as.factor(Policy_Analysis$marine_mech)
Implementation <- c("3"= "Marine specific", 
                    "2" = "Marine explicit",
                    "1" = "Marine Implicit", 
                    "0" = "No Policy")

policy_analysis_melt <- melt(Policy_Analysis, id.vars = 'OHI', variable.name = 'logGDP', value.name = 'Policy Type')




ggplot(data = Policy_Analysis, aes (x=OHI, y = log(GDP), color = marine_mech))+ 
  geom_point(data = specific, aes(x=OHI, y = log(GDP)), size = 2, shape = 19, color = "#009933") +
  geom_smooth(data = specific, method = "lm", color = "#009933") +
  geom_text(data = specific, aes(label= COUNTRY),size = 3.5, color="black", hjust =1, vjust = .5) +

  geom_point(data = implicit, aes(x=OHI, y = log(GDP)), size = 2, color = "#33FF99") +
  
  geom_point(data = none, aes(x=OHI, y = log(GDP)), size = 2, color = "grey50") +
  
  geom_point(data = explicit,aes(x=OHI, y = log(GDP)), size = 2, color = "#00CC66") +
  geom_smooth(data = explicit, method = "lm", color = "#00CC66") + #add  se= FALSE, to remove CI
  
  scale_fill_manual(values = Implementation)+

  xlab("Ocean Health Index") +
  ylab("logGDP") +
  theme_classic() +
  xlim(41, 100)
  

```


## Polity 2 vs GDP plot ---- Figure 4
```{r}

#install.packages("ggrepel")
#library(ggrepel)
  
ggplot(data = Policy_Analysis,
       aes (x=log(GDP), y = Polity2, color = marine_mech)) +
geom_point(data = specific, 
           aes(x=log(GDP), y = Polity2, color = "#009933"), color = "#009933", size = 11*(specific$Richness), shape = 19)+ 
geom_text(data = specific, 
          aes(label= COUNTRY),size = 4.5, color="black", hjust =0, vjust = -.5)+
geom_jitter(data = implicit, 
           aes(x=log(GDP), y = Polity2, color = "#33FF99"), color = "#33FF99", size = 11*(implicit$Richness))+
geom_jitter(data = none, 
           aes(x=log(GDP), y = Polity2, color = "grey50"), color = "grey50", size = 11*(none$Richness))+
geom_jitter(data = explicit, 
           aes(x=log(GDP), y = Polity2, color = "#00CC66"),color = "#00CC66", size = 11*(explicit$Richness))+

#geom_label(x=29, y=-2.5, label = "High capacity, Low implementation", size =5.5, vjust = -1, fill = "#d7191c", color = "black")+

#geom_label(x=29, y=11, label = "High capacity, High implementation", size =5.5, vjust = -1, fill = "#abd9e9", color = "black")+

#geom_label(x=24, y= -2.5, label = "Low capacity, Low implementation", size =5.5, vjust = -1, fill = "#fc8d59", color = "black")+

#geom_label(x=24, y=11, label = "Low capacity, High implementation", size =5.5, vjust = -1, fill = "#2c7bb6", color = "black")+

theme (text = element_text(family = "Arial"))+
xlab("log(GDP)") +
ylab("Polity2") +
ylim(-10, 13)+
xlim (22,31)+
geom_hline (yintercept = 0, color = "black") +
geom_vline(xintercept = 27, color = "black") +
theme_classic()+
theme(axis.text.x = element_text(size = 14), 
              axis.text.y = element_text(size = 14))
  #scale_color_manual("Policy Type", limits = c("Marine Explicit", "Marine Implicit", "No Policy", "Marine Specific"), 
                     #values = c("green", "red", "grey50", "blue")) +
  #guides(colour = guide_legend(override.aes = list(pch = c(16,21), fill = c("green", "red", "grey50", "blue"))))+
  

```


#Plot marine specific vs species Richness
```{r}
########Plot marine specific policies vs Richness ################# 
#trying to label just points over

  
ggplot(data = Policy_Analysis, aes (x=Richness, y = log(GDP)))+
  
  geom_text(aes(label = ifelse(Richness>.55, as.character(COUNTRY),'')), 
           size = 3.5, color="grey50", hjust =0, vjust = 0) +
  
  geom_point(data = explicit, aes(x=Richness, y = log(GDP)), size = 2, shape = 19, color = "#00CC66") +
  #geom_text(aes(label= COUNTRY),size = 3.5, color="black", hjust =1, vjust = .5) +
  geom_smooth(data = explicit, method = "lm", color = "#00CC66")+
  scale_y_continuous(expand=c(0,0)) + 
  scale_x_continuous(expand=c(0,0)) +


  geom_point(data = implicit, aes(x=Richness, y = log(GDP)), size = 2, color = "#33FF99") +

  geom_point(data = none, aes(x=Richness, y = log(GDP)), size = 2, color = "grey50") +
  
  geom_point(data = specific, aes(x=Richness, y = log(GDP)), size = 2, color = "#009933") +
  #geom_text(aes(label= COUNTRY),size = 3.5, color="black", hjust =1, vjust = .5) +
  geom_smooth(data = specific, method = "lm", color = "#009933") +
  
  
  xlab(" Marine Species Richness") +
  ylab("logGDP") +
  


  
  #scale_color_manual("Policy Type", limits = c("Marine Explicit", "Marine Implicit", "No Policy", "Marine Specific"), 
                    # values = c("green", "red", "grey50", "blue")) +
  #guides(colour = guide_legend(override.aes = list(pch = c(16,21), fill = c("green", "red", "grey50", "blue"))))+
  theme_classic()


```


